\begin{thebibliography}{9}

\bibitem{Codecademy} Codecademy - Learn to code interactively for free. \url{http://www.codecademy.com/}.

\bibitem{Coursera} Coursera - Take the world's best courses online, for free. \url{https://www.coursera.org/}.

\bibitem{Udacity} Udacity. \url{https://www.udacity.com/}.

\bibitem{SIETTE} Conejo, R., Guzmán, E., Millán, E., Trella, M., Pérez-de-la-Cruz, J. L., \& Rios, A. (2004). SIETTE: A Web-Based Tool for Adaptive Testing. \textit{International Journal of Artificial Intelligence in Education, 14}, 29-61.

\bibitem{CAT-Wiki} Computerized adaptive testing. \url{http://en.wikipedia.org/wiki/Computerized_adaptive_testing}. Accessed: \today.

\bibitem{CAT-Framework} Thompson, Nathan A., \& Weiss, David A. (2011). A Framework for the Development of Computerized Adaptive Tests. \textit{Practical Assessment, Research \& Evaluation}, 16(1).

\bibitem{CAT-Areas} IRT-Based CAT. \url{http://www.iacat.org/content/irt-based-cat}. Accessed: \today.

\bibitem{Weiss1984} Weiss, D. J., \& Kingsbury, G. G. (1984). Application of computerized adaptive testing to educational problems. \textit{Journal of Educational Measurement}, 21, 361-375

\bibitem{Weiss1985} Weiss, D.J. (1985). Adaptive Testing by Computer, \textit{Journal of Consulting and Clinical Psychology}. 1985, 53, 6, pp. 774-789.

\bibitem{CAT-Primer} Wainer, H., \& Mislevy, R.J. (2000). Item response theory, calibration, and estimation. In Wainer, H. (Ed.) Computerized Adaptive Testing: A Primer. Mahwah, NJ: Lawrence Erlbaum Associates.

\bibitem{IRT-Wiki} Item Response Theory. \url{http://en.wikipedia.org/wiki/Item_response_theory}. Accessed: \today.

\bibitem{Basics-IRT} Baker, Frank (2001). The Basics of Item Response Theory. (2nd Edition). Available at \url{http://info.worldbank.org/etools/docs/library/117765/Item\%20Response\%20Theory\%20-\%20F\%20Baker.pdf}. Accessed: \today.

\bibitem{Visual-IRT} Partchev, Ivailo (2004). A visual guide to item response theory. Available at \url{www.metheval.uni-jena.de/irt/VisualIRT.pdf}. Accessed: \today.

\bibitem{PAT} Chatzopoulou, D. I. \& Economides, A. A. (2010). Adaptive assessment of student's knowledge in programming courses. \textit{Journal of Computer Assisted Learning}, Vol. 26, No. 4.

\bibitem{SIETTE-small} Guzman, E.; Conejo, R., Self-assessment in a feasible, adaptive web-based testing system, Education, \textit{IEEE Transactions}, vol.48, no.4, pp.688,695, Nov. 2005.

\bibitem{SIETTE-components} E. Guzmán and R. Conejo, A brief introduction to the new architecture of SIETTE, in \textit{Lecture Notes in Computer Science. Proc. 3rd Adaptive Hypermedia Adaptive Web-based Systems (AH 2004)}, Berlin, Germany,
2004.

\bibitem{Interface-study} Christine Phillips \& Barbara S. Chaparro. Visual Appeal vs. Usability: Which One Influences User Perceptions of a Website More? \url{http://psychology.wichita.edu/surl/usabilitynews/112/aesthetic.asp}. Accessed: \today.

\bibitem{JavaFX} JavaFX - The Rich Client Platform. \url{http://www.oracle.com/technetwork/java/javase/overview/javafx-overview-2158620.html}. Accessed: \today.

\bibitem{Lister} Lister, R. (2001). Objectives and objective assessment in CS1. \textit{ACM SIGCSE Bulletin}, Vol. 33, No. 1, pp. 292-296.

\bibitem{Mitrovic} A. Mitrovic, “SINT—a symbolic integration tutor,” in \textit{Proc. 6th Int. Conf. Intelligent Tutoring Systems (ITS 2002), Lecture Notes in Computer
Science}, S. Cerri, G. Gouardères, and F. Paraguacu, Eds., New York, 2002, LNCS no. 2363, pp. 587–595.

\bibitem{JIT} JavaScript InfoVis Toolkit. \url{http://philogb.github.io/jit/}. Accessed: \today.

\bibitem{Beanshell} BeanShell - Lightweight Scripting for Java. \url{http://www.beanshell.org}. Accessed: \today.

\end{thebibliography}